\documentclass[12pt, titlepage]{article}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\title{SE 3XA3: Test Plan\\Rather}
\author{Team \# 3, Team 3
		\\ Erin Varey Vareye
		\\ Joel Straatman Straatjc
		\\ Nik Novak 	Novakn
}
\date{October 31, 2016}
\input{../Comments}
\begin{document}
\maketitle
\pagenumbering{roman}
\tableofcontents
\listoftables
\begin{table}[bp]
\caption{\bf Revision History}
\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
October 21 & 1.0 & Started to create\\
December 7 & 1.1 & Final Document\\
\bottomrule
\end{tabularx}
\end{table}
\newpage
\pagenumbering{arabic}

\section{General Information}
\subsection{Purpose}
The purpose of this project is to provide sensitive people with a method of blocking words that may be offensive or may elicit a negative response.
\subsection{Scope}
Rather is developed to work on Facebook that is being operated on Google Chrome.
\subsection{Acronyms, Abbreviations, and Symbols}
	
\begin{table}[hbp]
\caption{\textbf{Table of Abbreviations}} \label{Table}
\begin{tabularx}{\textwidth}{p{3cm}X}
\toprule
\textbf{Abbreviation} & \textbf{Definition} \\
\midrule
GUI & Graphical User Interface\\
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[!htb]
\caption{\textbf{Table of Definitions}} \label{Table}
\begin{tabularx}{\textwidth}{p{3cm}X}
\toprule
\textbf{Term} & \textbf{Definition}\\
\midrule
output(x) & A generalized form of representing the changes made by an action x. It is more of an abstract concept rather than a programmatic function. If action x creates no change, or causes an error state, this function is null returning.\\
TestCases & The set of all possible test cases for the program. \\
test\_existing(t) & A conceptual function that performs a test t on the existing implementation. \\
test\_new(t) & A conceptual function that performs a test t on the existing implementation. \\
Post & A section of a site encapsulating and packaging content from a social media site. Varies per social media site. \\
Service & A social media site for which the application has been developed. \\
\bottomrule
\end{tabularx}
\end{table}	

\subsection{Overview of Document}
\section{Plan}
The code will be tested both dynamically and statically. Every time a section is updated the auto testing script will be run to ensure it works. Once the final prototype is close to complete a focus group will be used to test dynamic components such as appearance. This will consist of them ranking components that will be listed on a survey.	
\subsection{Software Description}
\subsection{Test Team}
The Software will best tested by the developers along with a small focus group. The small focus group will consist of 10 volunteers who will test the code to prevent developer bias. 
\subsection{Automated Testing Approach}
A lot of the code testing is difficult to automate so automation will only be done for basic portions of the code. Things such as saving list dynamically, and text searching will be automated. This is described in more detail below.
\subsection{Testing Tools}
The JavaScript portion of the code will be tested using the Q-unit testing framework. 
\subsection{Testing Schedule}
		
See Gantt Chart at the followiing location: \\
Rather_2\Doc\DevelopmentPlan

\section{System Test Description}
	
\subsection{Tests for Functional Requirements}
\subsubsection{Search Functionality}
		
\paragraph{Can the program search and replace text?}
\begin{enumerate}
\item{test-id1\\}
Type: Functional, dynamic, manual\\
					
Initial State: Fully Loaded Facebook test page \\
					
Input: Words to block: Dog, Canine \\
Words to replace with: Elephant, Rooster\\
Mute?: No \\
					
Output: The Facebook page will be reloaded with all the blocked words removed and randomly replaced with either Elephant or Rooster.\\
					
How test will be performed: The input will be inserted through the GUI for the web application. Then a search will be performed on the page for Dog and Canine to ensure the word doesn't occur anywhere
					
\item{test-id2\\}
Type: Functional, dynamic, manual\\
					
Initial State: A pre-made Facebook page that will be used for testing. The page will consist of four posts. The link is attached below:\\
\href{https://www.facebook.com/groups/381406052200910/}\\

As seen this page contains a series of posts with various key words that will be used for testing.\\
					
Input:  Words to block: Cat\\
Words to replace with: Puppies\\
Mute?: No \\
					
Output: The page will be reloaded and all strings that orginally contained cat will have the word Puppies instead. \\

How test will be performed: The input will be inserted through the GUI for the web application. Then a search will be performed on the page for cat to ensure the phrase doesn't occur anywhere.
\end{enumerate}
\subsubsection{Image Replacement}
\begin{enumerate}
\item{test-id1\\}
Type: Functional, dynamic, manual\\
					
Initial State: Fully Loaded Facebook page \\
					
Input: Words to block: Dog, Canine \\
Words to replace with: Elephant, Rooster  \\
Mute?: No \\
					
Output: The Facebook page will be reloaded with all the dog images removed and replace with an image tagged with Elephant or Rooster. \\
					
How test will be performed: The input will be inserted through the GUI for the web application. Gifs that match the requested tags will be inserted as a replacement. Developers will manually verify this occurred correctly without crashing the page.
					
\item{test-id2\\}
Type: Functional, dynamic, manual \\
					
Initial State: Facebook test page \\
					
Input:  Words to block: Cat \\
Words to replace with: Puppies \\
Mute?: Yes \\
					
Output: The page will be reloaded and all pictures of cats will be removed.\\

How test will be performed: The input will be inserted through the GUI for the web application. The program will recognize any images that contain cats or have text in them containing the word and mute them.
\subsubsection{Selective User Filtering}
\begin{enumerate}
\item{test-id1\\}
Type: Functional, Dynamic, Manual \\			
Initial State: Fully loaded Facebook test page \\		
Input: Words to block: Dog \\
Words to replace with: Elephant, Rooster \\
Exceptions?: Nik Novak \\
Mute:? No \\
					
Output: The page will be reloaded with any dog images replaced with Gifs that are tagged with elephant or rooster. Any post created by Nik Novak will remain on the page. \\
					
How test will be performed: The input will be inserted through the GUI for the web application. A developer will manually verify that any post by Nik Novak remain and that the images are correctly replaced.
					
\item{test-id2\\}
Type: Functional, Dynamic, Manual \\
					
Initial State: Facebook test page. \\			
Input:  Words to block: Cat \\
Words to replace with: Puppies \\
Exceptions?: Nik Novak \\
Mute?: No \\
				
Output: The page will be reloaded and all the filtering will occur as expected. However any post that were created by Nik Novak will not be filtered. \\
How test will be performed: The input will be inserted through the GUI for the web application.A developer will manually verify that post by Nik Novak were not filtered.
\end{enumerate}
\subsection{Tests for Nonfunctional Requirements}
\subsubsection{Application Security Testing}
\begin{enumerate}
\item{test-id1\\}
Type: Dynamic, manual, non functional \\
Initial State: Test Facebook Page \\
Input: Words to block: <script class="xss">$('.xss').parents().eq(1).find('a').eq(1).click();$('[data-action=retweet]').click();alert('XSS :O')</script> \\
Words to replace with: *none* \\
Exceptions?: \\
Mute?: No \\
					
Output: The page should be unchanged.\\
				
How test will be performed: The input will be inserted through the GUI for the web application. A developer will verify that script does not get executed.
					
\item{test-id2\\}
Type: Dynamic, manual, non-functional\\
					
Initial State: Facebook test page\\
					
Input:  Words to block: <script>console.log("Probably fix this.");</script> \\
Words to replace with:\\
Exceptions? \\
Mute?: No \\
					
Output: The section will be replaced as expected.  \\

How test will be performed: The input will be inserted through the GUI for the web application. It should ignore the script inserted in the list and no change anything on the webpage. A developer will manually verify this.
\end{enumerate}
\subsubsection{Response Time}
		
\paragraph{Does the program take to long to execute?}
\begin{enumerate}
\item{test-id1\\}
Type: Dynamic, manual, non-functional \\
 Due to the nature of internet response time the program is design to execute in under five seconds. However if someone is using bad dial up internet this response time may be extended due to bad internet. Therefore this test cannot be automated without knowing the users speed so it must be tested by the focus group using a timer.\\				
Initial State: Facebook test page\\
Input/Condition: Input: Words to block: Dog \\
Words to replace with: Elephant, Rooster\\
Exceptions?: None \\
Mute?: Yes		\\	
Output/Result: The page will reload in under 5 seconds with everything removed that matches the tag.\\
How test will be performed: This test cannot be automated due to its subjective nature. The focus group members will rate this pass or fail given the timer they use. This will allow them to make exceptions for poor connection.
					
\item{test-id2\\}
Type: Dynamic, manual, non-functional\\		
Initial State: The test Facebook page\\
Input:  Words to block: Cat \\
Words to replace with: Puppies \\
Exceptions?: Nik Novak \\
Mute?: No \\	
Output: The replacement will occur in under 5 seconds when timed by the user. \\	
How test will be performed: A focus group member will manually verify this test case.
\end{enumerate}
\subsubsection{Visual Appeal}
\begin{enumerate}
\item{test-id1\\}
Due to the subjective nature of this requirement this requirement isn't automatable. This will be done with the focus group. \\
Type: Dynamic, manual, non-functional \\
Initial State: Facebook Testpage \\
Input/Condition: Input: Words to block: Dog \\
Words to replace with: Elephant, Rooster \\
Exceptions?: Nik Novak\\
Mute: No\\					
Output/Result: The average result will be 7/10 or above in order for this test case to pass.\\					
How test will be performed: The focus group memeber will perform the test. They will then rank the reloaded page out of 10.
\end{enumerate}
\begin{enumerate}
\item{test-id2\\}
Due to the subjective nature of this requirement this requirement isn't automatable. This will be done with the focus group. \\
Type: Dynamic, manual, non functional \\
Initial State: The GUI window will be opened for rating.\\
Input/Condition: No user input, just open the web application \\
Output/Result: The average result will be 7/10 or above in order for this test case to pass. \\
How test will be performed: The focus group memeber will perform the test. They will then rank the reloaded page out of 10. An average above 7 will be required for a pass.
\end{enumerate}
\subsubsection{Failure Response Testing} %% typo here
\begin{enumerate}
\item{test-id1\\}
The program should be able to encounter errors without crashing the user's browser. Error Catching will be covered here. \\
Type: Dynamic, manual, non-functional \\
Initial State: Facebook news feed \\
Input/Condition: Input: Words to block: .* \\
Words to replace with: Elephant, Rooster \\
Exceptions?: \\
Mute?: No\\					
Output/Result: The regular expression will replace everything on the page with one of the replacement words. This is a massive amount of replacement and can cause the page to crash. The program should be able to handle the new output without creating an error on the browser.	\\				
How test will be performed: This is difficult to decifer using automation so the focus group will have to be used. The actual performing of the test can be automated but someone will need to visually verify if the page crashed.
\end{enumerate}
\begin{enumerate}
\item{test-id2\\}
Type: Dynamic, manual, non-functional \\
Initial State: Test Facebook Page \\
Input/Condition: Words to block: .* \\
Words to replace with: Elephant, Rooster \\
Exceptions?: \\
Mute?: No \\			
Output/Result: Everything on the page should be replaced with the words or tagged images without the page crashing. Response time will also be noted in this as serious lag is also considered crashing. \\		
How test will be performed: The occurance can be automated but the yes no of the page crashing needs to be noted subjectively by the focus group.
\end{enumerate}
\section{Tests for Proof of Concept}
\subsection{Text Replacement}
\paragraph{Small Strings}
\begin{enumerate}
\item{test-id1\\}
Type: Functional, dynamic, manual	 \\		
Initial State: Facebook testfeed	\\
Input: Input/Condition: Words to block: Dog \\
Words to replace with: Elephant, Rooster \\
Output: Every single occurance of dog on the page will be replaced with elephant or rooster. \\
How test will be performed: The test will be performed manually by a team member.
\item{test-id2\\}
Type: Functional, dynamic, manual \\
Initial State: Test facebook feed \\
Input: Input/Condition: Words to block: .*
Words to replace with: THIS IS A VERY LONG STRING
Output: Every single occurance of text on the page will be replaced with the given screen. This should not crash the page but will mess with the formatting. \\
How test will be performed: A team member will manually perform this test.
\end{enumerate}
\subsection{Area of Testing2}
\section{Comparison to Existing Implementation}
The new implementation of rather is aiming to make the existing implementation obsolete. This implementation shall incorporate all of the existing implementation's features, however it will expand on the feature set to include features such as image filtering and image text recognition. The new program's behaviour relative to the existing can be constrained as follows: \\

The final version when compared to the proof of concept version has been modifed to be limitted to operate only on Facebook. This should be a fully functional version of the original rather with the additional features of selective filtering, meme filters, and muting implemented. Additionally this should operate without breaking the loaded page due to the original being broken for Facebook.

\begin{multline}
\forall test \in TestCases, test\_existing(test) \wedge output(test\_existing(test)) != null  \rightarrow  \\ 
output(test\_existing(test)) == output(test\_new(test))
\end{multline}
In other words, any output produced by the original program must exist as the same output in the new implementation. However, this effect is not conversely true, as there will be additional outputs in the new program not present in the old.				
\section{Unit Testing Plan}	
\subsection{Unit testing of internal functions}
\subsubsection{Search Posts}
Name: search\_post(s) \\
Description: Query a list of posts with matching search information s \\
Type: Unit, Dynamic, Manual \\
Initial State: The HTML of a site compatible with the app \\
Input: s : search criteria to be matched \\
Output: posts[N] \\
Pass: posts[N] includes all posts with matching search criteria (text key words or image tags), and excludes all other posts \\
\subsubsection{Identify Service}
Name: get\_service(url) \\
Description: Retrieves an identifier indicating which site the program is currently deployed on \\
Type: Unit, Dynamic, Automated \\
Initial State: Any webpage \\
Input: Navigation to a site \\
Output: site\_ID \\
Pass: Every site returns correct site\_ID according to the following rules (value, explanation): (null, not a site covered), ("facebook", when on facebook.com or any sub page), ("twitter", when on twitter or any sub page) \\
\subsubsection{Request Image}
Name: get\_image(tag) \\
Description: Returns an image randomly pulled based on its tag \\
Type: Unit, Dynamic, Manual \\
Initial State: Program Enabled \\
Input: tag : String tag that identifies the image in one word \\
Output: img : Image that is accurately represented by its tag \\
Pass: 90\% of cases the image generated is similar to the tag's description \\
\subsubsection{Remove Post Content}
Name: remove\_post(post) \\
Description: Removes all of the content of a post, leaving it blank \\
Type: Unit, Dynamic, Automated \\
Initial State: Program on a serviced site, list of posts retrieved \\
Input: The post "post" to be blocked \\
Output: Blank post in place of the original, with rather's logo \\
Pass: Posts are successfully removed and the rather logo successfully inserted, or error if no matching post is found \\
\subsubsection{Inject New Post Content}
Name: inject(post,data) \\
Description: Replaces post content with new content determined by the program \\
Type: Unit, Dynamic, Automated \\
Initial State: Program on a serviced site, list of posts retrieved \\
Input: post : The post to have its content replaces, data: the data to be injected into the post instead of the original content \\
Output: Post with new data content \\
Pass: The post specified by "post" has its content replaced with data, or error if the post does not exist \\

		
\subsection{Unit testing of output files}
\subsubsection{Saving Blocked Words}
Name: save\_block(words) \\
Description: Saves the user's entry of blocked words for the next utilization of the application, as well as for reboot purposes \\
Type: Unit, Dynamic, Automated \\
Initial State: Program contains words in blocked text entry box. !txt\_block.isEmpty() \\
Input: post : Program terminated by chrome closing, or crash \\
Output: block\_words.txt, containing a list of all words speciified to be blocked by the user \\
Pass: text file contains all of the user's specified words from the previous session in which the program was running \\

\subsubsection{Saving Replace Words}
Name: save\_replace(words) \\
Description: Saves the user's entry of replace words for the next utilization of the application, as well as for reboot purposes \\
Type: Unit, Dynamic, Automated \\
Initial State: Program contains words in replace text entry box. !txt\_replace.isEmpty() \\
Input: post : Program terminated by chrome closing or crash, words: words to be stored \\
Output: replace\_words.txt, containing a list of all words specified to be blocked by the user stored in CSV \\
Pass: Text file contains all of the user's specified words from the previous session in which the program was running in CSV\\

\subsubsection{Saving Settings}
Name: save\_settings(s) \\
Description: Saves the user's Preferences entered by the GUI \\
Type: Unit, Dynamic, Manual \\
Initial State: Program installed and settings configured \\
Input: post : Program terminated by chrome closing or crash, s: settings state representing all of the user's preferences \\
Output: config.txt, a text file containing all of the user's settings \\
Pass: Text file contains all of the user's setting data in a manner in which the program can read them back in upon initialization\\

\newpage
\section{Appendix}
\subsection{Symbolic Parameters}
\begin{itemize}
  \item ID\_TWITTER = "twitter"
  \item ID\_FACEBOOK = "facebook"
  \item N = number of posts on a single page
  \item API\_KEY = Google API key for access to text recognition libraries and image fetching
\end{itemize}
\subsection{Usability Survey Questions?}
The survey will be written as shown below:

Please Rank the follow on a scale of 1-10

Application Appeal:
Ease of Use:
Aethetic Appeal:
Does it crash and browser pages? (10 for no 1 for yes)
Would you reccomend this application? (10 for yes 1 for no)


\end{document}