\documentclass{article}
\usepackage{booktabs}
\usepackage{tabularx}
\title{SE 3XA3: Development Plan\\Title of Project}
\author{Team \#, Team Name
		\\ Erin Varey vareye
		\\ Nik Novak Novakn
		\\ Joel Straatman Straatjc
}
\date{}
\input{../Comments}
\begin{document}
\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 29 2016 & all & Created Development Plan\\

\bottomrule
\end{tabularx}
\end{table}
\newpage
\maketitle
Three university students have gotten together to revdelop Rather the web application. 
This development plan is going to hold us accountable. 
\section{Team Meeting Plan}
We are going to meet twice a week on Tuesday and Thursday evening's. 
Every team member is expected to bring an agenda with what they have accomplished and any issues they have encountered. 
Each section of code developed will be passed on to the tester team member to ensure it works correctly. 
Any member who misses a meeting without a valid excuse needs to buy the group a coffee. 
The meetings will be adjourned with a work plan of what everyone is expected to do until the next meeting.
\section{Team Communication Plan}
We will communicated through a variety of online methods.
We will use git to communicate code updates, facebook to set up meetings, skype for online meetings, and google docs to work on documentation before it is translated to latek.
\section{Team Member Roles}
Nik Novak- Lead developer
Erin Varey - Quality Assurance developer
Joel Straatman- Scrum Master
\section{Git Workflow Plan}
Within our git hierarchy we will have it split into code and documentation.
Every team member will pull the current code before working and then commit there changes every couple hours.
Within our documentation any documents that get multiple verisions will get their own folder.
The code will be broken up into functions that will be committed individually to make it easier to test and modularize. 
More subfolders in each branch will be created as needed.
\section{Proof of Concept Demonstration Plan}
The group has some experience with Javascript and has developed a basic test plan that the QA will implement after every change.
With regular meetings this code should be able to be completed in a reasonable timeframe. 
The scope of the project is small enough such that we can complete it and add additional features to continue to challenge ourselves.
\section{Technology}
This will be coded in Javascript and CSS using the IDE of choice.
Every group member have a computer to work on and commit to git with.
\section{Coding Style}
We will use a modular coding style and tabs not spaces.
The code will follow information hiding to ensure it is well designed.
We will test both blackbox and whitebox based on a test plan.
\section{Project Schedule}
Provide a pointer to your Gantt Chart.
\section{Project Review}
\end{document}