\documentclass{article}
\usepackage{booktabs}
\usepackage{tabularx}
\title{SE 3XA3: Development Plan\\Rather}
\author{Team 3
		\\ Erin Varey, vareye
		\\ Nik Novak, novakn
		\\ Joel Straatman, straatjc
}
\date{}
\input{../Comments}
\begin{document}
\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 29 2016 & all & Created Development Plan\\

\bottomrule
\end{tabularx}
\end{table}
\newpage
\maketitle
This development plan is a detailed structure of how we will redevelop Rather, an open source Chrome extension for replacing text and images on social media.
\section{Team Meeting Plan}
The team is going to meet twice a week on Tuesday and Thursday evening's for a maximum of 30 minutes. Every team member is expected to bring an agenda with what they have accomplished and any issues they have encountered. Each section of code developed will be passed on to the Quality Assurance developer for testing. Any member who misses a meeting without a valid excuse needs to buy the group a coffee. The meetings will be adjourned with a work plan of what everyone is expected to do until the next meeting. This will allow much of the coding to be done on each members time to ensure a quality job is done. Erin will be chairing group meetings and make notes of project progress.
\section{Team Communication Plan}
The group will communicate through a variety of online methods. We will use Git to communicate code updates, Facebook to set up meetings, Skype for online meetings, and Google Docs to work on documentation before it is translated to LaTeX.
\section{Team Member Roles}
\subsection{Nik Novak- Lead developer}
The role of the lead developer is to control the code segments as they are developed. Each member will develop various sections of the code but the role of the lead developer is to oversee each piece. They will assign sections to various members during the development process. They will also oversee each section to ensure it is being held to coding standard and style. 
\subsection{Erin Varey - Quality Assurance developer}
The QA developer will be the predominant tester of each code segment. As sections are completed the QA will thoroughly test each section to ensure it is robust and functional. When the QA develops sections of code the lead developer will be the tester. 
\subsection{Joel Straatman- Scrum Master}
The group will attempt to follow the scrum structure. The scrum master will oversee the whole process and keep up to date with various due dates. The scrum master will ensure the team follows the outline of goals as described in the Gantt chart and modify it as needed. 
\section{Git Workflow Plan}
Within our Git hierarchy it will split into code and documentation. Every team member will pull the current code before working and then commit their changes every couple hours. Within our documentation each required document will get its own folder. The code will be broken up into functions that will be committed individually to make it easier to test and modularize. More subfolders in each branch will be created as needed. The repo was created by Nik Novak, but will be maintained by each group member as equally as possible. Centralized Git workflow will be implemented, with individual branches being created when members are working on the same section. Each member will develop sections separately to avoid the need for merging. If this occurs branch names that consist of the section name and team member name and then will be merged once completed.
\section{Proof of Concept Demonstration Plan}
The group has some experience with JavaScript and has developed a basic test plan that the Quality Assurance developer will implement after every change. With regular meetings this code should be able to be completed in a reasonable timeframe. The scope of the project is small enough such that we can complete it and add additional features to continue to challenge ourselves. Each team member has previously completed small personal projects written in JavaScript, with one having produced a website relying heavily on JavaScript. Additional each member is well versed in how to use Google Chrome extensions once successfully completed. \\
\\
The Proof of Concept Demonstration will be a simplistic form of the application. It will be a text replacement application that will operate off of Google Chrome on any website. It won't have any features other than finding key words in a web pages text and replacing it with desired words. \\
\\
Some risks associated with this project include absent team members, tight deadlines, and legal issues. There is a risk team members may not complete their portions of the assignment correctly or on time causing damage to the entire group. Tight deadlines mean there is a chance a member may not finish their portion in time affecting the rest of the milestones on the Gantt chart. Lastly all though unlikely, due to API usage there may be issues with providers. For instance we will likely use a Google image recognition API which will identify what image is on the page. However if the application sends to many data request the company may not approve and pursue legal action. This is unlikely to happen but poses a risk.
\section{Technology}
This will be coded in JavaScript and CSS using the IDE of choice. Every group member has a computer to work on and commit to Git with. Automated testing will be done using Q-unit testing. Documents will be created using a Doxygen extension written in pearl that translates the code to Java and then documents it.
\section{Coding Style}
The group will model our coding style after Google; tabs for spacing code, constants written in all caps. The code will follow information hiding to ensure it is well designed. The group will test both black-box and white-box based on a test plan created by the Quality Assurance developer. Any scripting used for automation of testing will be written Q-unit a JavaScript framework.
\section{Project Schedule}
The Gantt Chart is located in the git repository under Master/doc/Development Plan.
\section{Project Review}
This project will be a good test of not only our skills in languages we have not formally learned yet, but also our ability to use our coding skills to create something usable in the real world. Up until now, the majority of Software Engineering students only have had experience with creating something that runs in an IDE. This project provides us with the interesting challenge of building upon our basic coding skills to create something that we and other people can use in their everyday lives. \\
\\
Now that the project is complete some modifications have been made to design structure. With all the additional features and fixes made compared to the original a decision was made to limit the scope of the project to Facebook. This was done to preserve information hiding in the code. A large number of third party API's are used to support features and implementing these on various social media websites while providing maintenance without breaking the code would be very difficult. The documents have been modified to reflect this. The end deliverable is a web application that filters images and text on Facebook. It has the option to mute or to replace these images with Gifs. The user can implement different kill list that they can switch between, and are saved in the application. Lastly the user has to option to selectively un-filter images from another user. Some areas that could have been improved in the project were team communication and group testing. The team meetings did not occur as regularly as desired and there wasn't a lot of group collaboration on documents. Lastly the focus group was small and the final product was only testing by ten users. We would have liked to have a variety of age groups and backgrounds test our application such as our Grandparents but didn't get the chance.

\end{document}