\documentclass[12pt, titlepage]{article}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\title{SE 3XA3: Test Report\\Title of Project}
\author{Team \# 3, Team 3
		\\ Erin Varey - vareye
		\\ Nik Novak - Novakn
		\\ Joel Straatmen - Straatjc
}
\date{\today}
\input{../Comments}
\begin{document}
\maketitle
\pagenumbering{roman}
\tableofcontents
\listoftables
\listoffigures
\begin{table}[bp]
\caption{\bf Revision History}
\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
December 5th & 1.0 & Starting Document\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}
\end{table}
\newpage
\pagenumbering{arabic}
This document ...
\section{Functional Requirements Evaluation}
\section{Nonfunctional Requirements Evaluation}
\subsection{Usability}
This section of the testing was performed using a survey from our focus group. The survey consisted of the following questions: \\
Please Rank the follow on a scale of 1-10 \\
Application Appeal:  \\
Ease of Use:\\
Aethetic Appeal: \\
Does it crash anybrowser pages? (10 for no 1 for yes) \\
Would you reccomended this application? (10 for yes 1 for no) \\
Additional comments? \\

10 people were surveyed in total. The results were over all positive with the average value of the results described below.	\\
\\
Name: Cameron
Application Appeal: 7 \\ 
Ease of Use: 7\\ 
Aethetic Appeal: 9\\ 
Does it crash anybrowser pages? (10 for no 1 for yes) 10\\ 
Would you reccomended this application? (10 for yes 1 for no) 10\\ 
Additional comments? I was impressed with all the images this could recognize. Wish I didn't have to refresh the page to reset it.\\

\\
Name: Josh
Application Appeal: 9 \\ 
Ease of Use: 8\\ 
Aethetic Appeal: 8\\ 
Does it crash anybrowser pages? (10 for no 1 for yes) 10\\ 
Would you reccomended this application? (10 for yes 1 for no) 10\\ 
Additional comments? I would definitely use this for my Facebook feed. I wish it worked on other social media websites like Twitter though.\\
\subsection{Performance}
\subsection{etc.}
	
\section{Comparison to Existing Implementation}	
This section will not be appropriate for every project.
\section{Unit Testing}
\section{Changes Due to Testing}
\section{Automated Testing}
		
\section{Trace to Requirements}
		
\section{Trace to Modules}		
\section{Code Coverage Metrics}

\end{document}